Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-07-18 ch04-lrmhinf/lrmhinf.tex
Stub: robust control

\paragraph*{Outline}
\label{par:lrmhinf:toc}
The problem is formulated in \secref{sec:lrmhinf:Problem}.
In \secref{sec:lrmhinf:LPMHinf} the proposed method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
In \secref{sec:lrmhinf:simulation} the method is illustrated on simulations, and the required measurement time is determined.
The technique is demonstrated on measurements of an \gls{AVIS} in \secref{sec:lrmhinf:measurement}.
Finally, the results and some challenges are discussed in \secref{sec:lrmhinf:conclusion}.

>>>>

\paragraph*{Outline}
\label{par:lrmhinf:toc}
In \secref{sec:lrmhinf:robust-control-basics}, a short introduction to robust control is linked to the work in this chapter.
The problem is formulated in \secref{sec:lrmhinf:Problem}.
In \secref{sec:lrmhinf:LPMHinf} the proposed method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
In \secref{sec:lrmhinf:simulation} the method is illustrated on simulations, and the required measurement time is determined.
The technique is demonstrated on measurements of an \gls{AVIS} in \secref{sec:lrmhinf:measurement}.
Finally, the results and some challenges are discussed in \secref{sec:lrmhinf:conclusion}.

\section{Intermezzo: Basics of Robust Control}
\label{sec:lrmhinf:robust-control-basics}
When designing a feedback controller $\Controller$ (as in \figref{fig:lrmhinf:tpc:nominal}), the goal is to design $\Controller$ such that the output $y$ of a plant $\true{\Plant}$ follows the command signal $r_2$ with some additional constraints on the performance of the whole closed-loop system (e.g. limited overshoot, short response times, good disturbance suppression, limited controller effort, \ldots).
This obviously requires knowledge of the actual plant $\true{\Plant}$ that is to be controlled.
Such knowledge can be obtained by means of modeling, be it first-principles modeling or system identification or a combination of modeling approaches, which provides an approximate model $\estimated{\Plant}$.

\begin{figure}[h]
 \centering
 \input{\thisDir/figs/tpc.tikz}
 \caption[Closed-loop block schematic.]{The considered feedback configuration $\ClosedLoop{\true{\Plant},\Controller}$.}
 \label{fig:lrmhinf:tpc:nominal}
\end{figure}

In classical control, the working assumption is that $\estimated{\Plant} = \true{\Plant}$ and hence the design of the controller is carried out on the estimated plant model.
This has the downside that if such a controller is not designed conservatively, errors in the model may produce instability or unwanted performance degradation.

\begin{figure}%[10]{R}[1em]{5cm}
  \centering
  \input{\thisDir/figs/modelset.tikz}
  \caption{The plant model set.}
  \label{fig:lrmhinf:modelset}
\end{figure}

In robust control~\citep{Zhou1996,Skogestad2005}, the design is carried out while taking uncertainties into account.
This is typically done by considering that the actual plant $\true{\Plant} \in \ModelSet[]$.
Hence, the problem is then to construct the model set $\ModelSet[]$ as illustrated in \figref{fig:lrmhinf:modelset}.
The design process thus guarantees performance and stability for the whole set instead of for a single model.
However, these guarantees hinge on proper specification of $\ModelSet[]$ which is typically done by estimating a nominal model $\estimated{\Plant}$ and the model uncertainty $\Delta(\estimated{\Plant}, \true{\Plant})$.
A generic way to express the plant model set (see also \figref{fig:lrmhinf:modelset}) is
\begin{equation}
  \ModelSet[]_{\mathrm{generic}} 
  \isdef 
  \Set{ \Plant | \norm{\Delta(\estimated{\Plant}, \Plant)} \leq \gamma}
  \equiv
  \Set{ \Plant(\estimated{\Plant}, \Delta) | \norm{\Delta} \leq \gamma}
  \label{eq:lrmhinf:model-set:generic}
\end{equation}
where both the norm and the concrete function $\Delta(\estimated{\Plant}, \Plant)$ are a choice for the control engineer.
An example of such a model set is easily imagined for additive uncertainty ($\Plant(\estimated{\Plant}, \Delta) = \estimated{\Plant} + \Delta$) when a $\Hardy_{2}$ norm is used, in that case one obtains
\begin{equation}
  \ModelSet[]_{\mathrm{additive,2}} = \Set{ \Plant | \norm[2]{\estimated{\Plant} - \Plant} \leq \gamma}
  \text{,}
\end{equation}
which is a multidimensional ball with radius $\gamma$.
Note that in many cases, the uncertainty structure (additive, multiplicative, \ldots) can be converted to other representations~\citep{Douma2005}.

Building a good model set $\ModelSet[]$ as in \eqref{eq:lrmhinf:model-set:generic}, hence requires estimating a good value of the overbound $\gamma$ to define the size of the set.
This overbound has important practical implications for the robust controller design.
Specifically, let us denote $\true{\gamma} \isdef \norm{\true\Delta} \isdef \norm{\Delta(\estimated{\Plant}, \true{\Plant})}$.
For an estimation procedure that yields the estimate $\estimated{\gamma}$ of the overbound, a few situations can hence occur.
\begin{itemize}
  \item $\estimated\gamma < \true{\gamma}$: the model set $\ModelSet[]$ is too small and hence $\true{\Plant} \not\in \ModelSet[]$.
  Based on such an estimate, the robust controller may fail to stabilize and perform well for the actual plant $\true{\Plant}$.
  \item $\estimated\gamma \gg \true{\gamma}$: the model set $\ModelSet[]$ is too big such that the robust controller is overly conservative.
  Consequently, the plant is still stabilized by the controller, but the performance of the system may be degraded.
  This  the actual plant is still stabilized by the controller, this can degrade the performance of the control system since it accounts for too many possible plants.
    \item $\estimated\gamma = \true{\gamma}$: the model set is just large enough to contain $\true{\Plant}$ such that both stability and performance are satisfied.
\end{itemize}

In robust control, it is most common to use a (possibly weighted) $\Hinf{}$ norm in the description of the plant model set~\citep{Skogestad2005,Zhou1996} such that
\begin{equation}
\ModelSet[] = \Set{ \Plant(\Delta, \estimated{\Plant}) | \norm[\infty]{\Delta 
} \leq \gamma}
  \text{,}
  \label{eq:lrmhinf:model-set:hinf}
\end{equation}
which is also the approach we follow in this chapter.
This $\Hinf{}$ norm can be interpreted as the peak gain of the model error $\Delta$, i.e. its maximum amplitude over the frequencies.
In control it is a common practice to use low-order models $\estimated{\Plant}$ to keep the controller design feasible, this means that $\Delta$ is often littered with unmodeled dynamics.
When those dynamics are resonant, it can be cumbersome to detect the respective peak amplitudes reliably from a short measurement dataset.
In this chapter, this problem will be tackled by exploiting the local models.
